% LaTeX resume
\documentclass{res}
\setlength{\textwidth}{5.1in} % width of text portion

\begin{document}

%put name at center
 \moveleft.5\hoffset\centerline{\large\bf Jayson S. Oldfather}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 %address
 \moveleft.5\hoffset\centerline{1595A Carlemont Drive}
 \moveleft.5\hoffset\centerline{Crystal Lake, IL 60014}
 \moveleft.5\hoffset\centerline{630.947.5299}
 \moveleft.5\hoffset\centerline{jayson@joldfather.com}

 \vspace{0.2in}
 \section{\centerline{PROFESSIONAL EXPERIENCE}}
 \vspace{8pt}
  {\bf Coilcraft} \hfill August 2006 - Present \\
  Cary, IL \hfill (Computer Programmer)
   \begin{itemize} \itemsep -2pt % this reduces space between items
    \item Develop cross-platform applications for Linux and Windows using wxWidgets and boost.
	\item Develop and maintain software that verifies all parts that go to the customer are within engineering specifications.
	\item Develop software using the ISO 9001 quality assurance requirements.
	\item Work with overseas customers to obtain software requirements and then develop features to specifications.
	\item Designed and implemented internal API for use across internal application suites.
	\item Implement software changes in tandem with machine hardware changes to meet shipping deadlines.
	\item Work with multiple projects to meet individual deadlines for each.
	\item Facilitated internal software migration from DOS to Windows XP / Vista / 7.
	\item Routinely collaborate with third party on designing tests for custom hardware.
   \end{itemize}

 \vspace{0.2in}
  \section{\centerline{EDUCATION}}
 \vspace{8pt}
 {\bf Bachelor of Science}, Computer Engineering Technology \\
 DeVry University, Addison, IL \hfill June 2006 \\
 Dean's List \\
 {\bf Senior Project} - Through the course of our final semester, we were involved in a project with 4 group members.  The group responsibilities were to write working versions of internet protocols for use on a Freescale microcontroller.

 \vspace{0.2in}
 \section{\centerline{COMPUTER \\ SKILLS}}
 \vspace{8pt}
 {\sl Languages:} C/C++, C\#, .NET Framework, CLISP, Perl \\
 {\sl Software:} Gentoo, Windows, Visual Studio, Vim, GCC, CMake

 \vspace{0.2in}
 \section{\centerline{HOBBIES}}
 \vspace{8pt}
 Japanese, Judo, Endurance sports

\end{document}
